---
title: "Analysis notebook: sedating medication use and injury-related events"
subtitle: "MEPS public use files"
date: last-modified
execute:
  echo: true
  warning: false
  eval: false
---

<!--
SCAFFOLD. execute.eval is false until the MEPS files are downloaded and the code is run.
Set eval: true in the YAML above once the pipeline runs end to end.
Nothing in this notebook may be presented as a result until it has actually run.
-->

Protocol for this analysis: [protocol.qmd](protocol.qmd). Read that first. This notebook implements it and adds nothing that is not specified there.

## Setup

```{r}
library(dplyr)
library(survey)
library(MEPS)      # remotes::install_github("e-mitchell/meps_r_pkg/MEPS")
library(gtsummary)

options(survey.lonely.psu = "adjust")

PANEL_YEAR <- 2021   # fix before running
```

## Load public files

```{r}
fyc  <- read_MEPS(year = PANEL_YEAR, type = "FYC")   # full year consolidated
rx   <- read_MEPS(year = PANEL_YEAR, type = "RX")    # prescribed medicines
er   <- read_MEPS(year = PANEL_YEAR, type = "ER")    # emergency room visits
ip   <- read_MEPS(year = PANEL_YEAR, type = "IP")    # inpatient stays
op   <- read_MEPS(year = PANEL_YEAR, type = "OP")    # outpatient visits
cond <- read_MEPS(year = PANEL_YEAR, type = "COND")  # medical conditions
clnk <- read_MEPS(year = PANEL_YEAR, type = "CLNK")  # condition-event link
```

## Exposure and comparator definitions

Fixed before any outcome is examined. Section 5 of the protocol.

```{r}
sedating_classes  <- c()   # therapeutic class codes, fill from MEPS RX codebook
comparator_classes <- c()  # non-opioid, non-sedating analgesic codes

# TODO: map TC1S1_1 / RXDRGNAM to the class lists above and freeze the mapping.
```

## Cohort construction

One row per inclusion or exclusion step, in protocol order.

```{r}
# TODO: build the attrition table. Each step reports n remaining.
# attrition <- tibble(step = character(), n = integer())
```

## Table 1

Weighted, standardized mean differences, no p-values.

```{r}
# design <- svydesign(ids = ~VARPSU, strata = ~VARSTR, weights = ~PERWT, data = cohort, nest = TRUE)
# tbl_svysummary(design, by = exposure, ...) %>% add_difference(test = everything() ~ "smd")
```

## Primary model

```{r}
# svyglm(injury_event ~ exposure + age + sex + ..., design = design, family = quasipoisson())
```

## Sensitivity analyses

Protocol Section 8, item 5. Narrow outcome, strict new-user rule, complete case.

```{r}
```

## Negative control outcome

```{r}
```

## Limitations

Reproduced from Section 9 of the protocol, unchanged. If the analysis revealed a limitation that was not anticipated, it is added here and labeled as post hoc.

## Reproducibility

```{r}
sessionInfo()
```
